Extended Data

### 2021-10-12 doc/manuscript/Dow_manuscript_Nature.Rmd
update manuscript with new multivariate analysis
#78

To test whether a positive effect of spring temperatures might be offset by a negative effect of summer temperatures, we tested for the joint and interactive effects of April and June-July $T_{max}$ on RWI.
Results were qualitatively similar to the univariate correlations (Fig. `r tree_rings`), with a positive effect of April $T_{max}$ for only **#**% of records and significant negative correlations with summer $T_{max}$ for **##**% of chronologies (`r EDT_tree_ring_summary`).
Significant interactive effects between spring and summer temperatures were rare (**##**% of chronologies).

>>>>

To test whether a positive effect of spring temperatures might be offset by a negative effect of summer temperatures, we tested for the joint effects of April and June-July $T_{max}$ on RWI.
Results were qualitatively similar to the univariate correlations (Fig. `r tree_rings`), with significant (at p = 0.05) positive correlations to April $T_{max}$ for only 7% of chronologies and significant negative correlations with June-July $T_{max}$ for 77% of chronologies (`r EDT_tree_ring_summary`).
